### 2023-06-08 resilience.tex
up
typo

Resilience and the home-space problem are also linked to the 
model-checking of the ``from-all'' formulae $\forall s \in X~ \exists t \in Y~ s \to^* t$
which has been shown decidable for Lossy Counter Machine
when $X$ and $Y$ are semi-linear sets~\cite{DBLP:conf/rp/Schnoebelen10}.
Other decidable formulae include ``one-to-one'' ($\exists s \in  X ~ \exists t \in  Y ~ s \to^* 
 t$), and ``all-to-same'' ($\exists t \in  Y ~ \forall s \in  X ~ s \to^*  t$),
whereas ``one-to-all'' ($\exists s \in  X ~ \forall t \in  Y ~ s \to^*  t$), 
``all-to-all'' ($\forall s \in  X ~ \forall t \in  Y ~ s \to^*  t$)
  and ``to-all'' ($\forall t \in  Y  ~ \exists s \in  X ~ s \to^*  t$) are undecidable (again, for Lossy Counter Machines).

@@

%		
We \alain{deduce} 
% \textcolor{red}{that the three resilience problems are decidable for all four pairs of sets $\Safe$ and $\Bad$ downward-closed and upward-closed sets.}
% \mathieu{changer ça}
decidability results for the four pairs of sets $\Safe$ and $\Bad$ downward-closed and upward-closed as seen in Section~\ref{synthesis}.

In particular, the existing proofs of resilience use the decidability of reachability; but we wish to decide resilience for models with undecidable reachability.
%
\alain{il manque un résultat d'indecidabilité pour les 3 resilience pour les WSTS+...}
%	 and ideals are recursive

>>>>

Resilience and the home-space problem are also linked to the 
model-checking of the ``from-all'' formula $\forall s \in X~ \exists t \in Y~ s \to^* t$
which has been shown decidable for Lossy Counter Machine
when $X$ and $Y$ are semi-linear sets~\cite{DBLP:conf/rp/Schnoebelen10}.
Other decidable formulae include ``one-to-one'' ($\exists s \in  X ~ \exists t \in  Y ~ s \to^* 
 t$), and ``all-to-same'' ($\exists t \in  Y ~ \forall s \in  X ~ s \to^*  t$),
whereas ``one-to-all'' ($\exists s \in  X ~ \forall t \in  Y ~ s \to^*  t$), 
``all-to-all'' ($\forall s \in  X ~ \forall t \in  Y ~ s \to^*  t$)
  and ``to-all'' ($\forall t \in  Y  ~ \exists s \in  X ~ s \to^*  t$) are undecidable (again, for Lossy Counter Machines).

@@

%		
We deduce 
% \textcolor{red}{that the three resilience problems are decidable for all four pairs of sets $\Safe$ and $\Bad$ downward-closed and upward-closed sets.}
% \mathieu{changer ça}
decidability results for the four pairs of sets $\Safe$ and $\Bad$ downward-closed and upward-closed as seen in Section~\ref{synthesis}.

In particular, the existing proofs of resilience use the decidability of reachability; but we wish to decide resilience for models with undecidable reachability.
%
\alain{il manque un résultat d'indecidabilité pour les 3 resilience pour les WSTS+...}
%	 and ideals are recursive 
Our result will rely on coverability instead of reachability. We moreover show undecidability when coverability is not decidable in the case $\Safe = \uparrow \Safe$.
